### 2013-09-19 manuscripts/reply/reply.tex
More work on reply.

For our re-analysis of the Philippines dataset we used the model-averaging
approach of \citet{Hickerson2013}, but with different prior models to avoid
mixing time units. We used five priors, all of which had priors on population
sizes of $\meanDescendantTheta{} \sim U(0.0001, 0.1)$ and
$\ancestralTheta{} \sim U(0.0001, 0.05)$.
Following \citet{Hickerson2013}, each of these priors had the following
priors on divergence time parameters:
$M_1$, $\divt{} \sim U(0, 0.1)$;
$M_2$, $\divt{} \sim U(0, 1)$;
$M_3$, $\divt{} \sim U(0, 5)$;
$M_4$, $\divt{} \sim U(0, 10)$; and
$M_5$, $\divt{} \sim U(0, 20)$.
For our prior, we simulated $1\e6$ random samples from each of the models
for a total sample of $5\e6$.
For each model, we retained the 10,000 samples with the smallest Euclidean
distance from the observed summary statistics, standardizing the statitics
using the prior means and standard deviations of the given model.
We then retained the 10,000 samples with the smallest Euclidean distance from
the observed summary statistics, this time standardizing the statistics using
the prior means and standard deviations across all five models.
We then repeated this analysis twice, replacing the $M_1$ with
$M_1A$ and $M_1B$, which differ only by having priors on divergence
times of $\divt{} \sim U(0, 0.01)$ and $\divt{} \sim U(0, 0.001)$,
respectively.
While we suspect the prior of $\divt{} \sim U(0, 0.1)$ used by
\citet{Hickerson2013} likely excludes the true divergence times of
at least some of the 22 taxa, we are nearly certain that these
narrower priors are incorrect and exclude the truth.

Our results show that the model-averaging approach of \citet{Hickerson2013}
does not reduce the methods bias towards models with smaller parameter space,
but rather allow it to manifest in a very dangerous way.
The method strongly prefers the prior model with the narrowest distribution on
divergence times across all three of our analyses, even when this model is
almost certainly incorrect and excludes the true divergence times of the
Philippine taxa.
Given that the results of \citet{Hickerson2013} strongly prefer the models with
the narrowest prior on divergence times, it seems quite likely that their
model-averaged results are dominated by models that exclude at least some of
the 22 true divergence times, making their results difficult to interpret.

@@

Our results show that the model-averaging approach of \citet{Hickerson2013}
excludes the true values of parameters in 97\% of the replicates (90\% with
GLM-regression adjustment), excluding upto 21 of the 22 true divergence times
(Figure~\ref{figExclusionSimTau}.
Furthermore, the posterior probability of excluding at least one true parameter
value is very high in nearly all of the replicates
(Figure~\ref{figExclusionSimProb}).
We used a Bayes factor (comparing models that exclude the truth to those that
do not) calculated for each replicate of greater than 10 as strong support for
excluding the truth.
With that criterion, 66\% of the replicats (87\% with GLM-regression adjustment)
strongly support the exclusion of true values (Figure~\ref{figExclusionSimProb}).

Given all of this, it is quite clear why one should use caution before
overly criticizing ones choice of priors after having seen the posterior.
This really is a strawman argument.
They were not there before the data were seen.

@@

>>>>

For our re-analysis of the Philippines dataset we used the model-averaging
approach of \citet{Hickerson2013}, but with different prior models to avoid
mixing time units. We used five priors, all of which had priors on population
sizes of $\meanDescendantTheta{} \sim U(0.0001, 0.1)$ and
$\ancestralTheta{} \sim U(0.0001, 0.05)$.
Following \citet{Hickerson2013}, each of these priors had the following
priors on divergence time parameters:
$M_1$, $\divt{} \sim U(0, 0.1)$;
$M_2$, $\divt{} \sim U(0, 1)$;
$M_3$, $\divt{} \sim U(0, 5)$;
$M_4$, $\divt{} \sim U(0, 10)$; and
$M_5$, $\divt{} \sim U(0, 20)$.
For our prior, we simulated $1\e6$ random samples from each of the models
for a total sample of $5\e6$.
For each model, we retained the 10,000 samples with the smallest Euclidean
distance from the observed summary statistics, standardizing the statistics
using the prior means and standard deviations of the given model.
We then retained the 10,000 samples with the smallest Euclidean distance from
the observed summary statistics, this time standardizing the statistics using
the prior means and standard deviations across all five models.
We then repeated this analysis twice, replacing the $M_1$ with
$M_1A$ and $M_1B$, which differ only by having priors on divergence
times of $\divt{} \sim U(0, 0.01)$ and $\divt{} \sim U(0, 0.001)$,
respectively.
While we suspect the prior of $\divt{} \sim U(0, 0.1)$ used by
\citet{Hickerson2013} likely excludes the true divergence times of
at least some of the 22 taxa, we are nearly certain that these
narrower priors are incorrect and exclude the truth.

Our results show that the model-averaging approach of \citet{Hickerson2013}
does not reduce the methods bias towards models with smaller parameter space,
but rather allow it to manifest in a very dangerous way.
The method strongly prefers the prior model with the narrowest distribution on
divergence times across all three of our analyses, even when this model is
almost certainly incorrect and excludes the true divergence times of the
Philippine taxa.
Unfortunately, ``checking'' the priors by plotting the summary statistics from
1000 random samples of each prior model along the first two orthogonal axes of
a principle component analysis, as recommended by \citet{Hickerson2013},
provides no warning of a problem (Figure~\ref{figPCA}.
Given that the results of \citet{Hickerson2013} strongly prefer the models with
the narrowest prior on divergence times, it seems quite likely that their
model-averaged results are dominated by models that exclude at least some of
the 22 true divergence times, making their results difficult to interpret.

@@

\highLight{Add how we determined exclusion.}
Our results show that the model-averaging approach of \citet{Hickerson2013}
excludes the true values of parameters in 97\% of the replicates (90\% with
GLM-regression adjustment), excluding up to 21 of the 22 true divergence times
(Figure~\ref{figExclusionSimTau}.
Furthermore, the posterior probability of excluding at least one true parameter
value is very high in nearly all of the replicates
(Figure~\ref{figExclusionSimProb}).
We used a Bayes factor (comparing models that exclude the truth to those that
do not) calculated for each replicate of greater than 10 as strong support for
excluding the truth.
With that criterion, 66\% of the replicats (87\% with GLM-regression adjustment)
strongly support the exclusion of true values (Figure~\ref{figExclusionSimProb}).

The results of our empirical and simulation-based analyses clearly demonstrate
the danger of using narrow, empirically guided priors in a Bayesian
model-averaging framework \ldots

\subsection*{Final thought on EB}
Given all of this, it is quite clear why one should use caution before
overly criticizing ones choice of priors after having seen the posterior.
This really is a strawman argument.
They were not there before the data were seen.

@@

\mFigure{../../model-choice/priors-for-pc-plot/pc-plots.pdf}{
    The graphical checks recommended by \citet{Hickerson2013} for three prior
    models: (A) $M_1$ ($\divt{} \sim U(0, 0.1)$), (B) $M_{1A}$ ($\divt{} \sim
    U(0, 0.01)$), and (C) $M_{1B}$ ($\divt{} \sim U(0, 0.001)$).
    The plots project the summary statistics from 1000 random samples from each
    model onto the first two orthogonal axes of a principle component analysis,
    with the blue dot representing the observed summary statistics from the 22
    population pairs of Philippine vertebrates.
}{figPCA}
